Population structure and phenotypic variation of \emph{Sclerotinia sclerotiorum} from dry bean (\emph{Phaseolus vulgaris}) in the United States

### 2017-11-17 doc/manuscript/paper.tex
run peerj-nitpick.sh

%% Submissions for peer-review must enable line-numbering
%% using the lineno option in the \documentclass command.
%%
%% Preprints and camera-ready submissions do not need
%% line numbers, and should have this option removed.
%%
%% Please note that the line numbering option requires
%% version 1.1 or newer of the wlpeerj.cls file, and
%% the corresponding author info requires v1.2

\documentclass[fleqn,10pt,lineno]{wlpeerj} % for journal submissions

% ZNK -- Adding headers for pandoc

\setlength{\emergencystretch}{3em}
\providecommand{\tightlist}{
\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{lipsum}
\usepackage[unicode=true]{hyperref}
\usepackage{longtable}

\usepackage{indentfirst}

\title{Population structure and phenotypic variation of \emph{Sclerotinia
sclerotiorum} from dry bean (\emph{Phaseolus vulgaris}) in the United
States}

\author[1]{Zhian N. Kamvar}

\author[1]{Bimal Sajeewa Amaradasa}

\author[1]{Rachana Jhala}

\author[1]{Serena McCoy}

\author[1]{James R. Steadman}

\author[1]{Sydney E. Everhart}

\corrauthor[1]{Sydney E. Everhart}{\href{mailto:everhart@unl.edu}{\nolinkurl{everhart@unl.edu}}}

\affil[1]{Department of Plant Pathology, University of Nebraska-Lincoln, Lincoln,
NE 68583}

%
% \author[1]{First Author}
% \author[2]{Second Author}
% \affil[1]{Address of first author}
% \affil[2]{Address of second author}
% \corrauthor[1]{First Author}{f.author@email.com}

%

\begin{abstract}
The ascomycete pathogen \emph{Sclerotinia sclerotiorum} is a
necrotrophic pathogen on over 400 known host plants, and is the causal
agent of white mold on dry bean. Currently, there are no known cultivars
of dry bean with complete resistance to white mold. For more than 20
years, bean breeders have been using white mold screening nurseries with
natural populations of \emph{S. sclerotiorum} to screen new cultivars
for resistance. It is thus important to know if the genetic diversity in
populations of \emph{S. sclerotiorum} within these nurseries a) reflect
the genetic diversity of the populations in the surrounding region and
b) are stable over time. Furthermore, previous studies have investigated
the correlation between mycelial compatibility groups (MCG) and
multilocus haplotypes (MLH), but none have formally tested these
patterns. We genotyped 366 isolates of \emph{S. sclerotiorum} from
producer fields and white mold screening nurseries surveyed over 10
years in 2003--2012 representing 11 states in the United States of
America, Australia, France, and Mexico at 11 microsatellite loci
resulting in 165 MLHs. Populations were loosely structured over space
and time based on analysis of molecular variance and discriminant
analysis of principal components, but not by cultivar, aggressiveness,
or field source. Of all the regions tested, only Mexico (n=18) shared no
MLHs with any other region. Using a bipartite network-based approach, we
found no evidence that the MCGs accurately represent MLHs. Our study
suggests that breeders should continue to test dry bean lines in several
white mold screening nurseries across the US to account for both the
phenotypic and genotypic variation that exists across regions.
% Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text. Dummy abstract text.
\end{abstract}

\usepackage{amsthm}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}{Lemma}[section]
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\theoremstyle{definition}
\newtheorem{example}{Example}[section]
\theoremstyle{definition}
\newtheorem{exercise}{Exercise}[section]
\theoremstyle{remark}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\begin{document}

\flushbottom
\maketitle
\thispagestyle{empty}

@@

\begin{figure}
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/mcg-subgraph-with-context.pdf}
\caption{Associations between Mycelial Compatibility Groups and
Multilocus Haplotypes. \textbf{A)} Barplot of Mycelial Compatibility
Group (MCG) abundance in descending order. Singletons (46) were
truncated, leaving 41 MCGs. White bars represent sample counts and grey
bars represent counts of unique multilocus haplotypes (MLH). The
transparency of the bars represent the evenness of the distribution of
the MLHs within a given MCG. A dashed box surrounds the eight most
common MCGs representing \textgreater{}~51\% of the data. \textbf{B)}
Full graph-representation of the relationship between MCGs (open
circles) and MLHs (filled circles). Details in Fig. \ref{fullgraph}.
\textbf{C)} A subset of \textbf{B} representing the 8 most common MCGs
and their associated MLHs (dashed box in \textbf{A}). Filled nodes
(circles) represent MLHs and open nodes represent MCGs. Node area scaled
to the number of samples represented (range: 1--73). Numbers inside
nodes are the MLH/MCG label (if n \textgreater{} 1). Edges (arrows)
point from MLH to MCG where the weight (thickness) of the edge
represents the number of shared isolates (range: 1--19). Edges extending
from MLHs displayed to other MCGs are not shown.}\label{biggraph}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/Figure7Z.pdf}
\caption{Biplot showing five most influential explanatory variables
(arrows) overlayed on the first two eigenvectors of distance based
redundancy analysis of \emph{Sclerotinia sclerotiorum} isolates. The
length of the arrows are directly proportional to the strength of the
correlation between explanatory and molecular variables. Open circles
represent the 318 clone-corrected haplotypes in ordination
space.}\label{rda-biplot}
\end{figure}

\begin{figure}
\centering
\includegraphics{../../results/figures/publication/aggressiveness.pdf}
\caption{Strip plot of aggressiveness by population arranged in
descending order of mean aggressiveness for all populations with N
\textgreater{} 5. White bars represent mean value. Circles represent
individual isolates where filled circles are isolates from white mold
screening nurseries (wmn) and open circles are isolates from producer
fields.}\label{aggressiveness-boxplot}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/mlg-11.pdf}
\caption{Network of populations (nodes/circles) and their shared
multilocus haplotypes (MLH) (edges/lines) genotyped over 11 loci. Each
node is labeled with \textbf{name (number of MLHs shared/number of MLHs
total).} The shade and area of the nodes are proportional to the number
of unique MLHs within the node and the inner nodes are proportional to
the number of private MLHs to the region (bottom legend). Each edge
represents a single MLH where its thickness represents the number of
populations that share the MLH and the shade represents the value of
\(P_{sex}\), or the probability of encountering that MLH from two
independent meiotic events.}\label{community-graph}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/DAPC.pdf}
\caption{Discriminant Analysis of Principal Components (DAPC) on regions
showing that Mexico is differentiated from other populations.
\textbf{A)} Scatter plot of first two components from DAPC. Points
represent observed individuals connected to the population centroids
with ellipses representing a 66\% confidence interval for a normal
distribution. The center of each component is represented as black grid
lines. \textbf{B)} Mean population assignment probability from the DAPC
for all populations with N \textgreater{} 10 (facets). Populations
represented along the horizontal axis and probability of assignment on
the vertical. Numbers next to source populations indicate population
size. All values sum to one.}\label{DAPC}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/dapc_region_year_micanewa.pdf}
\caption{Scatter plot of Discriminant Analysis of Principal Components
(DAPC) on Regions and Years showing non-differentiated temporal
variation NE and MI and temporal variation in WA and CA. Points (text
labels) represent observed individuals connected to the population
centroids with ellipses representing a 66\% confidence interval for a
normal distribution. The center of each component is represented as
black grid lines. A more detailed view is shown in Fig.
\ref{DAPC-RY-FULL}.}\label{DAPC-RY}
\end{figure}

@@

\subsection*{Funding}\label{funding}
\addcontentsline{toc}{subsection}{Funding}

Funding for this research was provided by the North Central Soybean
Research Program (\#639K623) to SEE, a Layman Award (\#2446) to SEE,
USDA-ARS National Sclerotinia Initiative (\#58-5442-2-209) to JRS/SEE,
and start-up funds from the University of Nebraska-Lincoln to SEE. The
funders had no role in study design, data collection and analysis,
decision to publish, or preparation of the manuscript.

@@

\subsection*{Conflicts of Interest}\label{conflicts-of-interest}
\addcontentsline{toc}{subsection}{Conflicts of Interest}

The authors declare no conflict of interest.

\subsection*{Author Contributions}\label{author-contributions}
\addcontentsline{toc}{subsection}{Author Contributions}

\begin{itemize}
\item
  \textbf{Zhian N. Kamvar} analyzed the data, contributed analysis
  tools, wrote the paper, prepared figures and tables, edited and
  reviewed drafts of the paper.
\item
  \textbf{B. Sajeewa Amaradasa} analyzed the data, contributed analysis
  tools, wrote drafts of the paper, edited and reviewed drafts of the
  paper.
\item
  \textbf{Rachana Jhala} Carried out experiments (MCG assessment,
  aggressiveness ratings, genotyping), edited and reviewed drafts of the
  paper.
\item
  \textbf{Serena McCoy} Carried out experiments (MCG assessment,
  aggressiveness ratings, genotyping), edited and reviewed drafts of the
  paper.
\item
  \textbf{James R. Steadman} Conceived and designed experiments,
  organized network of white mold screening nurseries, provided \emph{S.
  sclerotiorum} isolates, edited and reviewed drafts of the paper.
\item
  \textbf{Sydney E. Everhart} supervised data analysis, analyzed the
  data, contributed analysis tools, wrote the paper, edited and reviewed
  drafts of the paper.
\end{itemize}

\section*{Supplementary Information}\label{supplementary-information}
\addcontentsline{toc}{section}{Supplementary Information}

\setcounter{table}{0} \renewcommand{\thetable}{S\arabic{table}}
\setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}

\begin{longtable}[]{@{}lllrlr@{}}
\caption{\label{tab:isolate-table} Description of \emph{Sclerotinia
sclerotiorum} isolates used in this study. N = Number of Isolates. Key
abbreviations: wmn = white mold screening nursery, producer = producer
field, unk = unknown cultivar.}\tabularnewline
\begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Country\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\raggedright\strut
State\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\raggedright\strut
Field Code\strut
\end{minipage} & \begin{minipage}[b]{0.19\columnwidth}\raggedleft\strut
Year\strut
\end{minipage} & \begin{minipage}[b]{0.29\columnwidth}\raggedright\strut
Host\strut
\begin{minipage}[b]{0.11\columnwidth}\raggedright\strut
Country\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\raggedright\strut
State\strut
\end{minipage} & \begin{minipage}[b]{0.12\columnwidth}\raggedright\strut
Field Code\strut
\end{minipage} & \begin{minipage}[b]{0.19\columnwidth}\raggedleft\strut
Year\strut
\end{minipage} & \begin{minipage}[b]{0.29\columnwidth}\raggedright\strut
Host\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
USA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
wmn\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2004, 2005\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
Beryl, Bunsi, G122\strut
18\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
USA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
producer\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2007, 2010\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
Pinto, Yellow\strut
41\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
wmn\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2003\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
GH\strut
1\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
USA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
producer\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2003\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
GH\strut
1\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
USA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
wmn\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2003, 2004, 2005, 2008, 2009\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
11A, 37, 38, B07104, Beryl, Bunsi, Cornell, G122, Orion, PO7863,
WM31\strut
43\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
producer\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2003, 2008, 2009\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
BL, Black, Fuji, GH, Merlot, SR06233, unk, Vista, Zorro\strut
19\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
USA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
wmn\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2003, 2004\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
Beryl, Bunsi, G122\strut
11\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
USA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
producer\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2007, 2010\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
unk\strut
53\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
wmn\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2005\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
Beryl, Bunsi, G122\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
USA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
wmn\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2004, 2005, 2008, 2010\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
Beryl, Bunsi, G122, PO7683, unk\strut
27\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
producer\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2003, 2007, 2009, 2010\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
Beryl, Emerson, GH, Orion, Pinto, Weihing\strut
20\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
USA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
producer\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2003\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
GH\strut
1\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
USA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
wmn\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2003, 2004\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
Beryl, Bunsi, G122\strut
15\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
producer\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2003\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
G122, GH\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
USA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
wmn\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2003, 2004, 2005, 2008\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
11A, 37, 38, Beryl, Bunsi, Cornell, G122, Orion, PO7 104, PO7863,
WM31\strut
36\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
producer\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2003, 2007\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
GH, Merlot, Pinto, Redkid\strut
23\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
USA\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
producer\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2003\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
GH\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
wmn\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2005\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
Beryl, Bunsi, G122\strut
18\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
wmn\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2004, 2005\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
Beryl, Bunsi, G122\strut
18\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
producer\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2012\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
unk\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
wmn\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2004\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
Beryl, Bunsi, G122\strut
\begin{minipage}[t]{0.11\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
\strut
\end{minipage} & \begin{minipage}[t]{0.12\columnwidth}\raggedright\strut
producer\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft\strut
2004\strut
\end{minipage} & \begin{minipage}[t]{0.29\columnwidth}\raggedright\strut
Beryl\strut

\begin{longtable}[]{@{}cll@{}}
\caption{\label{tab:region-aggressiveness} Mean aggressiveness ratings for
Regions with more than five samples; groupings according to 95\%
family-wise confidence interval.}\tabularnewline
\toprule
\begin{minipage}[b]{0.14\columnwidth}\centering\strut
Region\strut
\end{minipage} & \begin{minipage}[b]{0.25\columnwidth}\raggedright\strut
Mean Aggressiveness\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\raggedright\strut
Group\strut
\end{minipage}\tabularnewline
\midrule
\endfirsthead
\toprule
\begin{minipage}[b]{0.14\columnwidth}\centering\strut
Region\strut
\end{minipage} & \begin{minipage}[b]{0.25\columnwidth}\raggedright\strut
Mean Aggressiveness\strut
\end{minipage} & \begin{minipage}[b]{0.08\columnwidth}\raggedright\strut
Group\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{0.14\columnwidth}\centering\strut
MN\strut
\end{minipage} & \begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
5.84\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
a\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering\strut
ND\strut
\end{minipage} & \begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
5.77\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
a\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering\strut
NE\strut
\end{minipage} & \begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
5.29\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
ab\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering\strut
MI\strut
\end{minipage} & \begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
5.13\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
abc\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering\strut
OR\strut
\end{minipage} & \begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
4.84\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
abcd\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering\strut
CO\strut
\end{minipage} & \begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
4.72\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
bcd\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering\strut
WA\strut
\end{minipage} & \begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
4.67\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
cd\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering\strut
France\strut
\end{minipage} & \begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
4.66\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
cd\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering\strut
Mexico\strut
\end{minipage} & \begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
4.58\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
cd\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering\strut
Australia\strut
\end{minipage} & \begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
4.12\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
cd\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{0.14\columnwidth}\centering\strut
CA\strut
\end{minipage} & \begin{minipage}[t]{0.25\columnwidth}\raggedright\strut
4.01\strut
\end{minipage} & \begin{minipage}[t]{0.08\columnwidth}\raggedright\strut
d\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

>>>>

@@

\begin{figure}
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/Fig1.pdf}
\caption{Associations between Mycelial Compatibility Groups and
Multilocus Haplotypes. \textbf{A)} Barplot of Mycelial Compatibility
Group (MCG) abundance in descending order. Singletons (46) were
truncated, leaving 41 MCGs. White bars represent sample counts and grey
bars represent counts of unique multilocus haplotypes (MLH). The
transparency of the bars represent the evenness of the distribution of
the MLHs within a given MCG. A dashed box surrounds the eight most
common MCGs representing \textgreater{}~51\% of the data. \textbf{B)}
Full graph-representation of the relationship between MCGs (open
circles) and MLHs (filled circles). Details in Fig. \ref{fullgraph}.
\textbf{C)} A subset of \textbf{B} representing the 8 most common MCGs
and their associated MLHs (dashed box in \textbf{A}). Filled nodes
(circles) represent MLHs and open nodes represent MCGs. Node area scaled
to the number of samples represented (range: 1--73). Numbers inside
nodes are the MLH/MCG label (if n \textgreater{} 1). Edges (arrows)
point from MLH to MCG where the weight (thickness) of the edge
represents the number of shared isolates (range: 1--19). Edges extending
from MLHs displayed to other MCGs are not shown.}\label{biggraph}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/Fig2.pdf}
\caption{Biplot showing five most influential explanatory variables
(arrows) overlayed on the first two eigenvectors of distance based
redundancy analysis of \emph{Sclerotinia sclerotiorum} isolates. The
length of the arrows are directly proportional to the strength of the
correlation between explanatory and molecular variables. Open circles
represent the 318 clone-corrected haplotypes in ordination
space.}\label{rda-biplot}
\end{figure}

\begin{figure}
\centering
\includegraphics{../../results/figures/publication/Fig3.pdf}
\caption{Strip plot of aggressiveness by population arranged in
descending order of mean aggressiveness for all populations with N
\textgreater{} 5. White bars represent mean value. Circles represent
individual isolates where filled circles are isolates from white mold
screening nurseries (wmn) and open circles are isolates from producer
fields.}\label{aggressiveness-boxplot}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/Fig4.pdf}
\caption{Network of populations (nodes/circles) and their shared
multilocus haplotypes (MLH) (edges/lines) genotyped over 11 loci. Each
node is labeled with \textbf{name (number of MLHs shared/number of MLHs
total).} The shade and area of the nodes are proportional to the number
of unique MLHs within the node and the inner nodes are proportional to
the number of private MLHs to the region (bottom legend). Each edge
represents a single MLH where its thickness represents the number of
populations that share the MLH and the shade represents the value of
\(P_{sex}\), or the probability of encountering that MLH from two
independent meiotic events.}\label{community-graph}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1.00000\textwidth]{../../results/figures/publication/Fig5.pdf}
\caption{Discriminant Analysis of Principal Components (DAPC) on regions
showing that Mexico is differentiated from other populations.
\textbf{A)} Scatter plot of first two components from DAPC. Points
represent observed individuals connected to the population centroids
with ellipses representing a 66\% confidence interval for a normal
distribution. The center of each component is represented as black grid
lines. \textbf{B)} Mean population assignment probability from the DAPC
for all populations with N \textgreater{} 10 (facets). Populations
represented along the horizontal axis and probability of assignment on
the vertical. Numbers next to source populations indicate population
size. All values sum to one.}\label{DAPC}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.61000\textwidth]{../../results/figures/publication/Fig6.pdf}
\caption{Scatter plot of Discriminant Analysis of Principal Components
(DAPC) on Regions and Years showing non-differentiated temporal
variation NE and MI and temporal variation in WA and CA. Points (text
labels) represent observed individuals connected to the population
centroids with ellipses representing a 66\% confidence interval for a
normal distribution. The center of each component is represented as
black grid lines. A more detailed view is shown in Fig.
\ref{DAPC-RY-FULL}.}\label{DAPC-RY}
\end{figure}

@@

@@
